Imposed form in the Early Acheulean? Evidence from Gona, Afar, Ethiopia

### 2024-08-10 manuscript/manuscript.Rmd
new figure testing.

date: "`r Sys.Date()`"
fontsize: 11pt
output: bookdown::pdf_document2
header-includes:
   - \usepackage{textcomp}
   - \usepackage{utopia}
   - \usepackage{lineno}
   - \usepackage[utf8]{inputenc}
   - \linenumbers
   - \usepackage{float}
   - \floatplacement{figure}{H}
   - \usepackage{caption}
   - \captionsetup[figure]{font=scriptsize}
   - \captionsetup[table]{font=scriptsize}
linestretch: 1.5
link-citations: yes
linkcolor: blue
bibliography: bibliography.bib
csl: apa.csl
editor_options: 
  markdown: 
    wrap: sentence
---

@@

```{r FAIBASE, echo=FALSE, out.width = '80%', fig.align='center', fig.cap="Mode 2 trends across blank types."}
knitr::include_graphics(here::here("figure/Fig.FAI by base.png"))
```

```{r FAIFLAKED, echo=FALSE, out.width = '80%', fig.align='center', fig.cap="Effect of FAI compared to unmodified large flakes from Acheulean contexts."}
knitr::include_graphics(here::here("figure/Fig.FAI by flaked.png"))
```

>>>>

date: "`r Sys.Date()`"
fontsize: 11pt
output: bookdown::pdf_document2
header-includes:
   - \usepackage{textcomp}
   - \usepackage{utopia}
   - \usepackage{lineno}
   - \usepackage[utf8]{inputenc}
   - \linenumbers
   - \usepackage{float}
   - \floatplacement{figure}{H}
   - \usepackage{caption}
   - \captionsetup[figure]{font=scriptsize}
   - \captionsetup[table]{font=scriptsize}
linestretch: 1.5
link-citations: yes
linkcolor: blue
bibliography: bibliography.bib
csl: frontiers.csl
editor_options: 
  markdown: 
    wrap: sentence
---

@@

```{r FAIBASE, echo=FALSE, out.width = '80%', fig.align='center', fig.cap="Mode 2 trends across blank types."}
knitr::include_graphics(here::here("figure/Fig.FAI by base new NEW.png"))
```

```{r FAIFLAKED, echo=FALSE, out.width = '80%', fig.align='center', fig.cap="Effect of FAI compared to unmodified large flakes from Acheulean contexts."}
knitr::include_graphics(here::here("figure/Fig.FAI by flaked new123.png"))
```
